---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

logged_data <- read_csv("~/Documents/stats220/project 2/gym_data.csv")

latest_data <- logged_data %>%
  rename(
    times = `How many times do you go to the gym per week? (0-10 times)`,
    gym_name = `Which gym do you usually go to?`,
    exercise = `What kind of exercise or weight loss activities do you usually do at the gym?`
        )

summary_min <- min(latest_data$times, na.rm = TRUE)
summary_max <- max(latest_data$times, na.rm = TRUE)
summary_mean <- mean(latest_data$times, na.rm = TRUE)

print(paste("Min (times):", summary_min))
print(paste("Max (times):", summary_max))
print(paste("Mean (times):", summary_mean))


gym_number <- ggplot(latest_data, aes(x = gym_name)) +
  geom_bar(fill = "skyblue") +
  labs(
    title = "Which Gym is the Most Popular",
    x = "Gym Name",
    y = "Number of Visits" 
) +
  theme_minimal() +
  coord_flip()

gym_exercise <- ggplot(latest_data, aes(x = exercise)) +
  geom_bar(fill = "coral") +
  labs(
    title = "Number of People by Exercise Type",
    x = "Exercise Type",
    y = "Number of People"
  ) +
  theme_minimal() +
  coord_flip()




```

```{css}

body{font-family:, sans-serif;
  line-height: 1.6;
  color: #333;
  background-color: #edc0ec;
  padding: 20px;
  
h2 {
  font-size: 2em;
  border-bottom: 2px solid #2980B9;
  padding-bottom: 5px;
  margin-bottom: 20px;
}




}


```

## My Gym Data Report

This report explores the gym habits of respondents. On average, people visited the gym `r summary_mean` times per week, with a minimum frequency of `r summary_min` visits and a maximum frequency of `r summary_max` visits.

### Data Description:

This data illustrates gym popularity among respondents. Clearly, the University of Auckland (UoA) Gym (Hiwa, Recreation Centre) is the most frequently visited, considerably surpassing other gyms. CityFitness is the second-most popular, while Jetts and apartment gyms have fewer users. The popularity of the UoA gym likely reflects the fact that most respondents are students at UoA, and its affordable annual membership cost (NZD 200) makes it particularly appealing to students.

```{r}
gym_number
```

### Exercise Data Description:

This bar chart shows the types of exercises respondents typically engage in at the gym. Clearly, strength training (e.g., using dumbbells and barbells) is the most preferred activity among gym-goers. The popularity of strength training might be due to its effectiveness in changing body composition, building muscle mass, and improving overall body shape, which is often a key motivation for gym attendance. In contrast, activities such as group fitness classes (e.g., Spin classes) and cardio equipment (e.g., treadmills) have fewer participants. This suggests respondents prioritize activities that provide more tangible and visible body transformation outcomes compared to general fitness and cardiovascular exercises.

```{r}
gym_exercise
```


```{r}
library(knitr)

summary_df <- data.frame(
  Statistic = c("Minimum", "Maximum", "Mean"),
  Value = c(summary_min, summary_max, summary_mean)
)

kable(summary_df, caption = "Summary Statistics for Gym Attendance")

library(knitr)

summary_df <- data.frame(
  Statistic = c("Minimum", "Maximum", "Mean"),
  Value = c(summary_min, summary_max, summary_mean)
)

```

In this data analysis, the minimum number of times users go to the gym per week is `r summary_min`, the maximum is `r summary_max`, and the average is `r summary_mean`.




